### 2023-11-11 main.tex
^^
Proof Psi' explicit

 By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 

@@

		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle=\sum_{\sigma\in \Omega}\Psi^{''}(\bm{\sigma})\prod_{x=1}^L\left[ \delta_{\tau_x,\mu_x}+\delta_{N,\mu_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$. 

@@

For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, 

@@

	c_{x}=\delta_{\sigma_{x},N}
thus, by using equation \eqref{ResulsBasis}, we have
	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\mu_{x}}^{(1-c_{x})}\left(1+\sum_{j=x}^{L}c_{j}\right)

@@

Therefore, using equation \eqref{ABS_intermediate} and observing that $c_{x}\delta_{\tau_{x},N} =\delta_{\tau_{x},N}$, we obtain 

@@

Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.

>>>>

 By considering a fixed $\bm{\tau}\in \Omega$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 

@@

		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega}\frac{1}{(1+L)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
	%	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
%where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$. 

@@

%For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, \\ \\ 

@@

	c_{x}(\sigma_{x})=\delta_{\sigma_{x},N}
To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain
	\Psi^{'}(\bm{\tau})%=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
	=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
%Consider the factor $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}$ in the above equation. When $\sigma_{x}\neq N$ (then $c_{x}=0$) and $\tau_{x}\neq N$, it becomes $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})$. On the other hand, when $\sigma_{x}=N$ (then $c_{x}=1$)  and $\tau_{x}\neq N$, then it becomes $1$. Finally, if $\sigma_{x}=N$ and $\tau_{x}=N$ it becomes $0$. Therefore, we can replace it by $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}$. It follows that 
We observe that, for all $x\in \{1,\ldots,L\}$,
	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\\
	=&\begin{cases}
		(\alpha_{\tau_{x}}-\beta_{\tau_{x}})+\beta_{\tau_{x}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad &\text{if}\quad \tau_{x}= N
	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
Therefore we have that
\Psi^{'}(\bm{\tau})%=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
%=&\frac{1}{(1+L)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
%thus, by using equation \eqref{ResulsBasis}, we have
	%\Psi^{''}(\bm{\sigma})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\sigma_{x}}^{(1-c_{x})}\left(1+\sum_{j=x}^{L}c_{j}\right)

@@

Observing that $c_{x}(1-\delta_{\tau_{x},N}) =c_{x}-\delta_{\tau_{x},N}$, we finally obtain

@@

Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
